---
title: "FDD3451"
author: "Hong"
date: "2024-03-01"
output:
  word_document: default
  html_document: default
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, class.source = "watch-out",
                      fig.width=3, fig.height=3,fig.align='left',
                      fig.pos = "H")
```

#### Loading packages
```{r, include=FALSE}
pkgs = c("tidyverse","hablar","sjmisc","xlsx","gplots","smplot2", "Seurat","openxlsx",
         "readxl","MuSiC","SingleCellExperiment","reshape2","cowplot","bseqsc")
for (i in pkgs){
  if(! i %in% installed.packages()){
    BiocManager::install(i, ask = F, update = F)
  }
}
invisible(lapply(pkgs, function(x) library(x, character.only=TRUE)))
rm(pkgs, i)
```


- Reproduce the code provided in paper
- Compare the influence of different measures on the output
- Compare to other method

#### Material and method
1 - Reproducibility

Trough a step-by-step replication of the MUSIC tutorial,I got most of code run successfully but encountered challenges with function bulk_construct(). This function is used for the last step of 'Estimation of cell type proportions with pre-grouping of cell types', which handles the colinearity in bulk sequencing data due to closely related cell types in solid tissues. 

```{r, include=FALSE}
### Bulk RNA-seq
GSE50244.bulk.eset = readRDS('data/GSE50244bulkeset.rds')
bulk.mtx = exprs(GSE50244.bulk.eset)
bulk.meta = phenoData(GSE50244.bulk.eset)@data
#### Single-cell
EMTAB.sce = readRDS('data/EMTABesethealthy.rds')
```

2 - Robustness of MUSIC

2.1 - Tuning parameters - Threshold of convergence (eps)

```{r, include=FALSE}
# Estimate cell type proportions
# Create dataframe for beta cell proportions and HbA1c levels
res = ''
Est.prop.list = list()
eps = c(0.1, 0.01, 0.001, 0.0001)
for(i in eps){
  Est.prop.res = music_prop(bulk.mtx = bulk.mtx, 
                               sc.sce =  EMTAB.sce,
                               eps = i,
                               clusters = 'cellType',
                               samples = 'sampleID', 
                               select.ct = c('alpha', 'beta', 'delta', 'gamma',
                                             'acinar', 'ductal'), verbose = F)
  m.prop.ana = data.frame(
    pData(GSE50244.bulk.eset)[rep(1:89, 1),
                              c('age', 'bmi', 'hba1c', 'gender')],
    ct.prop = Est.prop.res$Est.prop.weighted[, 2],
    eps = paste0('eps: ', i),
    Method = 'MuSiC'
  ) %>% rownames_to_column(., var = 'Sample')
  colnames(m.prop.ana)[1:5] = c('Sample','Age', 'BMI', 'HbA1c', 'Gender')
  m.prop.ana = subset(m.prop.ana,!is.na(HbA1c))
  m.prop.ana$Disease = factor(c('Normal', 'T2D')[(m.prop.ana$HbA1c > 6.5) + 1], c('Normal', 'T2D'))
  m.prop.ana$D = (m.prop.ana$Disease == 'T2D') / 5
  
  res = rbind(res, m.prop.ana)
}

res = res[-1,]

p1 = res %>%            
  convert(num(HbA1c, ct.prop, D)) %>% 
  convert(chr(eps)) %>% 
  ggplot(., aes(HbA1c, ct.prop)) + 
  #geom_smooth(method = 'lm',  se = FALSE, col = 'black', lwd = 0.25) +
  sm_statCorr() +
  geom_point(aes(fill = eps, color = Disease, stroke = D,
                 shape = Disease), size = 2, alpha = 0.7) +  
  facet_wrap(~ eps) + 
  ggtitle('HbA1c vs Beta Cell Type Proportion') + theme_minimal() + 
  scale_colour_manual( values = c('white', "gray20")) + 
  scale_shape_manual(values = c(21, 24))
```

2.2 - Tuning parameters - nu

```{r, include=FALSE}
# Estimate cell type proportions
# Create dataframe for beta cell proportions and HbA1c levels
res = ''
Est.prop.list = list()
nu = c(1e-02, 1e-04, 1e-06, 1e-08)
for(i in nu){
  Est.prop.res = music_prop(bulk.mtx = bulk.mtx, 
                               sc.sce =  EMTAB.sce,
                               nu = i,
                               clusters = 'cellType',
                               samples = 'sampleID', 
                               select.ct = c('alpha', 'beta', 'delta', 'gamma',
                                             'acinar', 'ductal'), verbose = F)
  m.prop.ana = data.frame(
    pData(GSE50244.bulk.eset)[rep(1:89, 1),
                              c('age', 'bmi', 'hba1c', 'gender')],
    ct.prop = Est.prop.res$Est.prop.weighted[, 2],
    nu = paste0('nu: ', i),
    Method = 'MuSiC'
  ) %>% rownames_to_column(., var = 'Sample')
  colnames(m.prop.ana)[1:5] = c('Sample','Age', 'BMI', 'HbA1c', 'Gender')
  m.prop.ana = subset(m.prop.ana,!is.na(HbA1c))
  m.prop.ana$Disease = factor(c('Normal', 'T2D')[(m.prop.ana$HbA1c > 6.5) + 1], c('Normal', 'T2D'))
  m.prop.ana$D = (m.prop.ana$Disease == 'T2D') / 5
  
  res = rbind(res, m.prop.ana)
}

res = res[-1,]

p1 = res %>%            
  convert(num(HbA1c, ct.prop, D)) %>% 
  convert(chr(nu)) %>% 
  ggplot(., aes(HbA1c, ct.prop)) + 
  #geom_smooth(method = 'lm',  se = FALSE, col = 'black', lwd = 0.25) +
  sm_statCorr() +
  geom_point(aes(fill = nu, color = Disease, stroke = D,
                 shape = Disease), size = 2, alpha = 0.7) +  
  facet_wrap(~ nu) + 
  ggtitle('HbA1c vs Beta Cell Type Proportion') + theme_minimal() + 
  scale_colour_manual( values = c('white', "gray20")) + 
  scale_shape_manual(values = c(21, 24))

compar = list(c("nu: 0.01", "nu: 1e-04"), c("nu: 1e-06", "nu: 1e-04"), c("nu: 1e-04", "nu: 1e-08"))
p2 = res %>%            
    convert(num(HbA1c, ct.prop, D)) %>% 
    convert(chr(nu)) %>% 
    ggplot(., aes(nu, ct.prop)) + geom_boxplot(outlier.color = NA) + 
  geom_jitter(aes(color = Disease),position = position_dodge2(width = .5)) + 
  theme_minimal() + theme(legend.position = 'right',
                          axis.text = element_text(size = 9, color = 'black'),
                          axis.title.x = element_blank()) + 
  stat_compare_means(comparisons = compar)

ggsave(p1, file = 'cell.pro.nu.tunning.pdf', width = 6, height = 4)
ggsave(p2, file = 'cell.pro.nu.tunning.box.pdf.pdf', width = 4, height = 3.2)
```
2.3 - Tuning parameters - iter.max

```{r, include=FALSE}
# Estimate cell type proportions
# Create dataframe for beta cell proportions and HbA1c levels
res = ''
Est.prop.list = list()
iter = c(500, 800, 1000, 1200)
for(i in iter){
  Est.prop.res = music_prop(bulk.mtx = bulk.mtx, 
                               sc.sce =  EMTAB.sce,
                               iter.max = i,
                               clusters = 'cellType',
                               samples = 'sampleID', 
                               select.ct = c('alpha', 'beta', 'delta', 'gamma',
                                             'acinar', 'ductal'), verbose = F)
  m.prop.ana = data.frame(
    pData(GSE50244.bulk.eset)[rep(1:89, 1),
                              c('age', 'bmi', 'hba1c', 'gender')],
    ct.prop = Est.prop.res$Est.prop.weighted[, 2],
    iter = paste0('iter: ', i),
    Method = 'MuSiC'
  ) %>% rownames_to_column(., var = 'Sample')
  colnames(m.prop.ana)[1:5] = c('Sample','Age', 'BMI', 'HbA1c', 'Gender')
  m.prop.ana = subset(m.prop.ana,!is.na(HbA1c))
  m.prop.ana$Disease = factor(c('Normal', 'T2D')[(m.prop.ana$HbA1c > 6.5) + 1], c('Normal', 'T2D'))
  m.prop.ana$D = (m.prop.ana$Disease == 'T2D') / 5
  
  res = rbind(res, m.prop.ana)
}

res = res[-1,]

p1 = res %>%            
  convert(num(HbA1c, ct.prop, D)) %>% 
  convert(chr(iter)) %>% 
  ggplot(., aes(HbA1c, ct.prop)) + 
  #geom_smooth(method = 'lm',  se = FALSE, col = 'black', lwd = 0.25) +
  sm_statCorr() +
  geom_point(aes(fill = iter, color = Disease, stroke = D,
                 shape = Disease), size = 2, alpha = 0.7) +  
  facet_wrap(~ iter) + 
  ggtitle('HbA1c vs Beta Cell Type Proportion') + theme_minimal() + 
  scale_colour_manual( values = c('white', "gray20")) + 
  scale_shape_manual(values = c(21, 24))

compar = list(c("iter: 500", "iter: 1000"), c("iter: 800", "iter: 1000"), c("iter: 1200", "iter: 1000"))
p2 = res %>%            
    convert(num(HbA1c, ct.prop, D)) %>% 
    convert(chr(iter)) %>% filter(iter == 'iter: 500' | iter == 'iter: 1000') %>% 
    select(ct.prop, iter, Sample) %>% spread(iter, ct.prop) %>% 
  ggplot(., aes(`iter: 1000`, `iter: 500`)) +
  geom_point(color = 'lightblue') +
  theme_bw() + theme(legend.position = 'right',
                          axis.text = element_text(size = 9, color = 'black')) 
p3 = res %>%            
    convert(num(HbA1c, ct.prop, D)) %>% 
    convert(chr(iter)) %>% filter(iter == 'iter: 1200' | iter == 'iter: 1000') %>% 
    select(ct.prop, iter, Sample) %>% spread(iter, ct.prop) %>% 
  ggplot(., aes(`iter: 1000`, `iter: 1200`)) +
  geom_point(color = 'lightblue') +
  theme_bw() + theme(legend.position = 'right',
                          axis.text = element_text(size = 9, color = 'black')) 
ggsave(p1, file = 'cell.pro.iter.tunning.pdf', width = 6, height = 4)
ggsave(p2+p3, file = 'cell.pro.iter.tunning.corr.pdf.pdf', width = 6, height = 2.5)
```
2.4 - Influence of gene numbers on the MUSIC prediction

```{r, include=FALSE}

bulk.meta$Disease = factor( c('Normal', 'T2D')[(bulk.meta$hba1c > 6.5) + 1], c('Normal', 'T2D'))
### table random samples by group: T2D or normal
gene_size = c(.1, .3, .5, .8, 1)
# Create dataframe for beta cell proportions and HbA1c levels
res = ''
j = 1
for(i in 1:length(gene_size)) {
  set.seed(567)
  Est.prop.res = music_prop(
    bulk.mtx = bulk.mtx %>% as.data.frame() %>% sample_frac(gene_size[i]) %>% as.matrix(),
    sc.sce =  EMTAB.sce,
    eps = i,
    clusters = 'cellType',
    samples = 'sampleID',
    select.ct = c('alpha', 'beta', 'delta', 'gamma',
                  'acinar', 'ductal'),
    verbose = F
  )
  m.prop.ana = data.frame(
    pData(GSE50244.bulk.eset)[,
                              c('age', 'bmi', 'hba1c', 'gender')],
    ct.prop = Est.prop.res$Est.prop.weighted[, 2],
    Size = paste0(gene_size[i]*100, '% ','genes'),
    Method = 'MuSiC'
  ) %>% rownames_to_column(., var = 'Sample')
  colnames(m.prop.ana)[1:5] = c('Sample','Age', 'BMI', 'HbA1c', 'Gender')
  m.prop.ana = subset(m.prop.ana, !is.na(HbA1c))
  m.prop.ana$Disease = factor( c('Normal', 'T2D')[(m.prop.ana$HbA1c > 6.5) + 1], c('Normal', 'T2D') )
  m.prop.ana$D = (m.prop.ana$Disease == 'T2D')/5

  res = rbind(res, m.prop.ana)
  j = j + 1
}

res = res[-1,]

res %>%
  convert(num(HbA1c, ct.prop, D)) %>% 
  convert(chr(Size)) %>% 
  mutate(Size = factor(Size, levels = c("10% genes","30% genes",
                                        "50% genes", "80% genes", "100% genes"))) %>% 
  ggplot(., aes(HbA1c, ct.prop)) + 
  #geom_smooth(method = 'lm',  se = FALSE, col = 'black', lwd = 0.25) +
  sm_statCorr() + 
  geom_point(aes(fill = Size, color = Disease, stroke = D,
                 shape = Disease), size = 2, alpha = 0.7) +  
  facet_wrap(~ Size, nrow = 1, ncol = 5) + 
  ggtitle('HbA1c vs Beta Cell Type Proportion') + theme_minimal() + 
  scale_colour_manual( values = c('white', "gray20")) + 
  scale_shape_manual(values = c(21, 24))
```

2.4 (test) Influence of samples size on the MUSIC prediction

```{r, include=FALSE}

bulk.meta$Disease = factor( c('Normal', 'T2D')[(bulk.meta$hba1c > 6.5) + 1], c('Normal', 'T2D'))
### table random samples by group: T2D or normal
sample_size = c(.8, .9)
# Create dataframe for beta cell proportions and HbA1c levels
res = ''
j = 1
for(i in 1:length(sample_size)) {
  set.seed(567)
  bulk_selected = bulk.meta %>% rownames_to_column(., 'ID') %>% group_by(Disease) %>% sample_frac(sample_size[i])
  Est.prop.res = music_prop(
    bulk.mtx = bulk.mtx[,bulk_selected$ID],
    sc.sce =  EMTAB.sce,
    clusters = 'cellType',
    samples = 'sampleID',
    select.ct = c('alpha', 'beta', 'delta', 'gamma',
                  'acinar', 'ductal'),
    verbose = F
  )
  m.prop.ana = data.frame(
    pData(GSE50244.bulk.eset)[bulk_selected$ID,
                              c('age', 'bmi', 'hba1c', 'gender')],
    ct.prop = Est.prop.res$Est.prop.weighted[, 2],
    Samplesize = paste0('Sample Size', sample_size[i]*100, '%'),
    Method = 'MuSiC'
  ) %>% rownames_to_column(., var = 'Sample')
  colnames(m.prop.ana)[1:5] = c('Sample','Age', 'BMI', 'HbA1c', 'Gender')
  m.prop.ana = subset(m.prop.ana, !is.na(HbA1c))
  m.prop.ana$Disease = factor( c('Normal', 'T2D')[(m.prop.ana$HbA1c > 6.5) + 1], c('Normal', 'T2D') )
  m.prop.ana$D = (m.prop.ana$Disease == 'T2D')/5

  res = rbind(res, m.prop.ana)
  j = j + 1
}

res = res[-1,]

res %>%
  convert(num(HbA1c, ct.prop, D)) %>% 
  convert(chr(Size)) %>% 
  mutate(Size = factor(Size, levels = c("10% genes","30% genes",
                                        "50% genes", "80% genes", "100% genes"))) %>% 
  ggplot(., aes(HbA1c, ct.prop)) + 
  #geom_smooth(method = 'lm',  se = FALSE, col = 'black', lwd = 0.25) +
  sm_statCorr() + 
  geom_point(aes(fill = Size, color = Disease, stroke = D,
                 shape = Disease), size = 2, alpha = 0.7) +  
  facet_wrap(~ Size, nrow = 1, ncol = 5) + 
  ggtitle('HbA1c vs Beta Cell Type Proportion') + theme_minimal() + 
  scale_colour_manual( values = c('white', "gray20")) + 
  scale_shape_manual(values = c(21, 24))
```
2.5 Performance of MUSIC on in-house data

```{r, include=FALSE}

meta_gather = function(){
  meta = read.csv(file = paste0(workdir,'/01.Data/_OLINK_and_RNAseq_samples_by_Diagnosis.all.csv')) %>% 
    select(Patient.Code,BMI, FIB.4.Index,
           Age..in.years., Albumin..g.dL., ALT..IU.L., AST..IU.L.,
           Platelets..x10.9., NASH.score, VIRUS, Aetiology,
           Fibrosis.Stage, BCLC.Score, AFP, VIRUS)
  return(meta)
}

workdir = '../../../00-ResearchProjects/00-SysMedicine/NAFLD/LiverDisease'
load(paste0(workdir, '/VIRALNASHARLD_HCC/06.Deconlution/tissue.Rdata'))
load(paste0(workdir, '/01.Data/LiverDisease.ran.seq.txi.Rdata'))
count_bulk = txi_kallisto$counts %>% as.data.frame()
tissue1 = CreateSeuratObject(counts = tissue@data, meta.data = tissue@meta.data)
load(paste0(workdir, '/VIRALNASHARLD_HCC_3/02.Results/Olink_proteomics.STAT.limma.Rdata'))
meta_RNA = read.csv(paste0(workdir, '/01.Data/_OLINK_and_RNAseq_samples_by_Diagnosis.RNA.csv')) %>% 
  select(U, ID)
mathched_RNA = olink$metadat %>%
  left_join(meta_gather(), by = c("U" = "Patient.Code")) %>% 
  filter(!is.na(Fibrosis.Group.in.paper)) %>% 
  left_join(meta_RNA) %>% 
  filter(Fibrosis.Group.in.paper != 'Healthy') %>% 
  mutate(Fibrosis.Group.in.paper = case_when(
    Fibrosis.Group.in.paper == 'F0-2' ~ 'F02',
    TRUE ~ Fibrosis.Group.in.paper
  ))

count_bulk = count_bulk %>% dplyr::select(mathched_RNA$ID)
#Idents(object = tissue1) = "liver"
#tissue1 = subset(x = tissue1, idents = c('Cirrhotic1', 'Cirrhotic2', 'Cirrhotic3',
#                                       'Cirrhotic4','Cirrhotic5'),invert = FALSE)
Idents(tissue1) = 'annotation_indepth'
markers_genes <- FindAllMarkers(tissue1, 
                                log2FC.threshold = 0.2, 
                                test.use = "wilcox",
                                min.pct = 0.1, 
                                min.diff.pct = 0.2, 
                                only.pos = TRUE, 
                                max.cells.per.ident = 50,
                                assay = "RNA")

linage2markers = markers_genes %>%
  filter(p_val_adj < 0.05)

sec = as.SingleCellExperiment(tissue1)
########## Find out common genes
c.genes = sort(intersect(rownames(count_bulk), rownames(sec)))
sec = sec[c.genes,]
count_bulk = as.matrix(count_bulk[c.genes,])
########## using common genes
clusters.type = as.character(unique(sec$annotation_indepth))
names(clusters.type) = clusters.type

Est.prop.res = music_prop(bulk.mtx = count_bulk, 
                               sc.sce =  sec,
                               clusters = 'annotation_indepth',
                               samples = 'dataset')

pdf('cell.pro.pdf', width = 6, height = 2.5)

Heatmap(Est.prop.res$Est.prop.weighted, show_row_names = F, column_names_gp  = gpar(fontsize = 7), 
        show_column_dend = F, col = colorRamp2(c(0,0.001, 1), c(alpha("#C7522B",0.1), alpha("#BBC297", 0.1),alpha("#3C5941", 0.1))),
        name = 'Pro.')
dev.off()
```

3.1 and 3.2 DWLS, reproducibility and gene number influence
```{r}
setwd("DWLS-master/ISC")

#load packages and functions
source("DWLS-master/Deconvolution_functions.R")
load('prediction.DWLS.Rdata')

all_res = ''
genesize = c(0.1, 0.3, 0.5, 0.8, 1)
for(i in genesize) {
  bulkData.sub1  = sample_frac(as.data.frame(bulkData[, 1:30]), i)
  colnames(bulkData.sub1) = colnames(bulkData)[1:30]
  #allCounts_DWLS <- NULL
  #allCounts_OLS <- NULL
  allCounts_SVR <- NULL
  
  for (j in 1:(dim(bulkData.sub1)[2])) {
    print(colnames(bulkData.sub1)[j])
    S <-
      sig.matrix.mean %>% column_to_rownames(., var = 'gene') %>% as.matrix()
    Bulk <- bulkData.sub1[, j] # extract every sample
    names(Bulk) <- rownames(bulkData.sub1)
    Genes <- intersect(rownames(S), names(Bulk))
    S = S[Genes, ]
    Bulk <- Bulk[Genes]
    #solOLS <- solveOLS(S, Bulk)
    #solDWLS <- solveDampenedWLS(S, Bulk)
    solSVR <- solveSVR(S, Bulk)
    
    #allCounts_DWLS <- cbind(allCounts_DWLS, solDWLS)
    #allCounts_OLS <- cbind(allCounts_OLS, solOLS)
    allCounts_SVR <- cbind(allCounts_SVR, solSVR)
  }
  
  colnames(allCounts_SVR) <- colnames((bulkData.sub1))
  allCounts_SVR = allCounts_SVR %>% as.data.frame() %>% 
    rownames_to_column(., var = 'cell_type') %>% 
    mutate(gene_size = paste0(i*100, '%'))
  all_res = rbind(all_res, allCounts_SVR)
}

all_res = all_res[-1,]

meta = read.csv('../../../00-ResearchProjects/00-SysMedicine/NAFLD/LiverDisease/01.Data/_OLINK_and_RNAseq_samples_by_Diagnosis.RNA.csv') %>% select(ID, FIB.4.Index)

mappingDF = read.xlsx('../../../00-ResearchProjects/00-SysMedicine/NAFLD/LiverDisease/VIRALNASHARLD_HCC/06.Deconlution/results/EMS84316-supplement-Suppl_Table_8 nno.xlsx')

p3 = all_res %>% gather(ID,percentage,-c(cell_type, gene_size)) %>% left_join(meta) %>% 
  filter(cell_type == 'Hepatocytes') %>%
  convert(num(percentage, FIB.4.Index)) %>% 
  filter(percentage != 0) %>% 
  mutate(gene_size = factor(gene_size, levels = c("10%", "20%",
                                                  "30%","50%","80%", "100%"))) %>% 
  ggplot(., aes(log(FIB.4.Index), percentage)) + 
  #geom_smooth(method = 'lm',  se = FALSE, col = 'black', lwd = 0.25) +
  sm_statCorr(label_y = 0.7, text_size = 3) + 
  geom_point(aes(color = gene_size), size = 2, alpha = 0.7) +  
  facet_wrap(~ gene_size, nrow = 1, ncol = 5) + 
  ggtitle('FIB-4 vs Hepatocytes Proportion') + theme_minimal() + 
  scale_shape_manual(values = c(21, 24))
ggsave(p3, file = 'cell.pro.geneSize.DWLS.pdf', width = 8, height = 2.5)
```

3.3 and 3.4 DWLS, (https://github.com/dtsoucas/DWLS)
```{r}
allCounts_DWLS<-NULL
allCounts_OLS<-NULL
allCounts_SVR<-NULL

for(j in 1:(dim(bulkData)[2])){
  print(colnames(bulkData)[j])
    S<- sig.matrix.mean %>% column_to_rownames(., var = 'gene') %>% as.matrix()
    Bulk<-bulkData[,j] # extract every sample
    names(Bulk)<-rownames(bulkData)
    Genes<-intersect(rownames(S),names(Bulk))
    S = S[Genes,]
    Bulk<-Bulk[Genes]
    solOLS<-solveOLS(S,Bulk)
    solDWLS<-solveDampenedWLS(S,Bulk)
    solSVR<-solveSVR(S,Bulk)

    allCounts_DWLS<-cbind(allCounts_DWLS,solDWLS)
    allCounts_OLS<-cbind(allCounts_OLS,solOLS)
    allCounts_SVR<-cbind(allCounts_SVR,solSVR)
}

mappingDF = read.xlsx(paste0(workdir, '/VIRALNASHARLD_HCC/06.Deconlution/results/EMS84316-supplement-Suppl_Table_8 nno.xlsx'))
resuktpred = Est.prop.res$Est.prop.weighted %>% as.data.frame() %>% 
  select_if(colSums(.) != 0) %>% 
  rownames_to_column(., var = 'ID') %>% 
  gather(cell.type, pro, -ID) %>% 
  convert(num(pro)) %>% 
  left_join(mathched_RNA) %>% 
  left_join(mappingDF, by = c("cell.type" = 'annotation_indepth')) %>%
  mutate(cluster = factor(cluster, levels = unique(cluster)))
metadata = olink$metadat %>%
  left_join(meta_gather(), by = c("U" = "Patient.Code")) %>% 
  filter(!is.na(Fibrosis.Group.in.paper)) %>% 
  left_join(meta_RNA) %>% 
  filter(Fibrosis.Group.in.paper != 'Healthy') %>% 
  select(ID, Fibrosis.Group.in.paper, BMI, `Albumin..g.dL.`, 
         `ALT..IU.L.`, `AST..IU.L.`, `Platelets..x10.9.`, `FIB.4.Index`) %>% 
  set_colnames(c("ID", "Fibrosis.Group.in.paper","BMI", 
                 "Albumin", "ALT","AST","Platelets","FIB4"))

resuktpred = metadata %>% select(ID, Fibrosis.Group.in.paper) %>%
  left_join(
    allCounts_SVR %>% as.data.frame() %>%
      rownames_to_column(., var = 'cell.type') %>%
      gather(ID, pro,-cell.type) %>% convert(num(pro))
  ) %>%
  mutate(cell.type = str_replace_all(cell.type, '_', ' ')) %>%
  mutate(cell.type = str_replace_all(cell.type, '([0-9])', '(\\1)')) %>%
  left_join(mappingDF, by = c("cell.type" = 'annotation_indepth')) %>%
  mutate(cluster = factor(cluster, levels = unique(cluster)))
 
prep_stacked_bar = resuktpred %>% 
  mutate(Fibrosis.Group.in.paper = factor(Fibrosis.Group.in.paper, 
                              levels = c("F4","F3","F0-2"))) %>% 
    ggplot(., aes(Fibrosis.Group.in.paper, pro)) +
    geom_col(aes(fill = cluster),
             position = 'fill') +
    scale_y_continuous(expand = range(0,0)) +
    theme_classic() + 
    scale_fill_manual(values = alpha(hcl.colors(44, palette = "Fall"),0.5)) +
    labs(y = 'Cell Proportion', x = '', fill = 'Cell Cluster') +
    plot_theme('nogrid') +
    theme(axis.text = element_text(size = 7, color = 'black'),
          axis.title = element_text(size = 8, color = 'black')) +
  coord_flip()

ggsave(prep_stacked_bar, file = 'decon.prediction.DWLS.pdf',
       width = 7.3, height = 2.8)
```


